Example Manuscript Template for a Data Analysis Project

### 2021-09-17 products/manuscript/Manuscript.Rmd
.

## General Background Information
During the COVID-19 pandemic, the government of Bangladesh adopted nationwide lockdown. There has been some studies that showed its adverse  effect on people of Bangladesh. As the government has taken the vaccination program very strictly, it was expected to see a large number of population would get vaccinated. But as the reality was the opposite, we wanted to know why people are not getting vaccinated enough despite being affected by COVID-19 lockdown. Our research will shed somelight on Bangladeshi people's vaccine hesitancy. Als briefly, out work will present its relation to mental wellness.

@@

## Questions/Hypotheses to be addressed
The main question is to find out why people gets hesitant to get vaccinated. Finding out their key motivator is the prime goal. Also, how mental wellness after covid-19 lockdown might affect their hesitant desition to get vaccinated, is another question we want to answer.

>>>>

## General Background Information
During the COVID-19 pandemic, the government of Bangladesh adopted nationwide lockdown.\ There has been some studies that showed its adverse  effect on people of Bangladesh.\ As the government has taken the vaccination program very strictly, it was expected to see a large number of population would get vaccinated.\ But as the reality was the opposite, we wanted to know why people are not getting vaccinated enough despite being affected by COVID-19 lockdown.\ Our research will shed somelight on Bangladeshi people's vaccine hesitancy. Als briefly, out work will present its relation to mental wellness.

@@

## Questions/Hypotheses to be addressed
The main question is to find out why people gets hesitant to get vaccinated.\ Finding out their key motivator is the prime goal.\ Also, how mental wellness after covid-19 lockdown might affect their hesitant desition to get vaccinated, is another question we want to answer.\
